\section{The Mass Lattice Construction}

The empirical success of the logarithmic mass index motivates a geometric reformulation of the particle mass spectrum. Rather than treating the index $q$ as a one-dimensional ordering parameter, we embed it into a discrete lattice structure associated with the representation theory of the alternating group $A_5$.

\subsection{Logarithmic Mass Index}

Let $m_i$ denote the pole mass of a fundamental particle and $m_e$ the electron mass. We define the dimensionless mass index
\begin{equation}
q_i = \mathrm{Round}\!\left(\frac{\log(m_i/m_e)}{\log \varphi}\right),
\quad \varphi = \frac{1+\sqrt{5}}{2}.
\end{equation}

For all known Standard Model particles, the resulting $q_i$ values are stable under experimental uncertainties and lie extremely close to integers. This defines the empirical mass scaling relation
\begin{equation}
m_i \approx m_e \, \varphi^{q_i},
\end{equation}
which holds over more than twelve orders of magnitude in mass.

\subsection{Lattice Embedding}

The group $A_5$ admits irreducible representations of dimensions $3$, $4$, and $5$. We associate these representations with orthogonal lattice directions and define integer coordinates $(a_i,b_i,c_i)\in\mathbb{Z}^3$ such that
\begin{equation}
q_i = a_i + 2b_i + 3c_i.
\end{equation}

This mapping is not assumed \emph{a priori}, but is instead inferred by requiring that:
\begin{itemize}
\item each known particle is assigned a unique lattice site,
\item particles of similar type cluster geometrically,
\item the embedding is minimal in dimension.
\end{itemize}

The resulting construction yields an injective mapping of all known fermions and gauge bosons into a bounded region of $\mathbb{Z}^3$.

\subsection{Geometric Interpretation}

Each particle corresponds to a discrete lattice site, while its physical mass is encoded in the logarithmic height $q$. The lattice therefore represents a quantized mass geometry rather than a continuous hierarchy. Empty lattice sites represent admissible mass values not yet occupied by known particles, immediately suggesting testable predictions.
